Hot and fresh: Pervasive climate stressors of seagrass in a large Gulf coast estuary

### 2023-08-25 manu-draft.qmd
add pyro refs for discussion

## Acknowledgments {.unnumbered}

>>>>

OTB seagrass loss and role of pyrodinium, optimal temperatures from 28-31 [@lopez2021]. For salinity, highest growth rates at 24 psu and above, with decline in growth rates at 20 psu [@usup1994], in Florida growth has occurred in psu 10-45, bloom concentrations observed above 15 psu [@phlips2006; @lopez2021].

## Acknowledgments
